---
Title: "stringi: Fast and Portable Character String Processing Facilities"
author: "Write your name"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
--- 

<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;} 
div.comment {background-color:#F0F6FF; border-radius: 5px; padding: 20px;}
</style> 

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
``` 

Text manipulation using stringi 

(a) Fetch the list of political slogans from this page ("https://en.wikipedia.org/wiki/List_of_political_slogans"). Use following (xpath_expression <- "//div[contains(@class, 'mw-heading mw-heading3') or contains(@class, 'mw-heading mw-heading4')]/following-sibling::ul[1]/li")  

Use stringi for the following tasks

(b) Sort the fetched data alphabetically 

(c) Apply the padding operation to ensure that all the strings have same width and store them in a variable 

(d) Change the case of the slogans 

(e) Count number of times the word power appears in these slogans 

(d) Extract and  slogans with following words- Power, Power and People, Power or People 

(e) Find the slogans where a word is followed or preceded by specific phrase 

(f) Create a datframe with two columns- Slogans and their Descriptions. Convert first Alphabets of both the variables in capital letter  

```{r}


``` 
 

```{r}

```

