---
title: "Advanced String Processing with Stringi"
subtitle: "Live Workshop Session"
author:
  - Benedict Anderer
  - Farhan Shaikh 
institute: "**Hertie School of Governance, Berlin**"
date: "2024/10/28 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    includes:
      after_body: hertie_logo.html
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
      hash: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Outline
1. Text as Data in R
--
<br>
2. The Role of String Processing in Political Science
--
<br>
3. Introducing Stringi & Friends
--
<br>
4. Match Made in Heaven: Stringi & Regex
--
<br>
6. Stringi: Key Features & Use Cases
--
<br>
6. Further Resources 

---
#Introducing Stringi & Friends
##String processing in the tidyverse

- `stringi`: most comprehensive string processing package (250 functions)
--
<br>
  - commands begin with `stri`
  - less accessible, but can handle advanced tasks
- `stringr`: built on top of `stringi`
--
<br>
  - more accessible, but "only" 49 functions
  - commands begin with `str`


- Bullet 3

---
## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

